Abb Analysis

### 2017-02-08 abbDataAnalysis_Script.Rmd
initial add of Logit Model

>>>>

  ss60 <- which(str.data.ic$cancel.policy == 'Super Strict 60 Days')
  str.data.ic$cancel.policy[ss60] <- 'Strict'
  cpmiss <- which(str.data.ic$cancel.policy == '')
  str.data.ic <- str.data.ic[-cpmiss, ]

  ps <- which(str.data.ic$host.type == 'Profit Seeker')
  os <- which(str.data.ic$host.type == 'Opportunistic Sharer')
  mu <- which(str.data.ic$host.type == 'Multi-Platform User')
  un <- which(str.data.ic$host.type == 'Unknown')

  mod.str <- glm(str.pot.pref~type+as.factor(bedbath)+
                    sub.mrkt+
                    I(max.guests/bedrooms)+min.stay+
                    I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                 family=binomial(link='logit'),
                 data=str.data.ic[un,])
